---
title: "Adding starpower"
output: html_document
date: "2023-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries

```{r cars}
library(tidyverse)
library(dplyr)
```

## Loading the file
The file has been provided by my thesis supervisor. The data is scraped the 13th of april 2023

```{r}

starPower <- read_csv("../../data/datasets/superstar_persons.csv")

```

##Getting a feel for the data
First of all we find that the rank does not matchup with the number of variables.

```{r}
starPower %>%
  summarize(min_rank = min(Rank),
            max_rank = max(Rank),
            min_earnings = min(earnings),
            max_earnings = max(earnings))
```

Some names appear multiple times, however with different identifiers. This suggests that a person has fulfilled different roles and therefore gets another identifier.  

```{r}

starPower %>%
  group_by(primaryName, Rank, earnings) %>%
  filter(n() > 1)

```

After some research by typing the nconst of randomly selected actors directily into IMDb (https://www.imdb.com/name/nm.../) I found that the the different identifiers still lead to the same actor, often a slightly different page. The only thing dat differs is the column "primaryProfession".

```{r}
starPower %>%
  filter(!grepl('actor|actress', primaryProfession, ignore.case = TRUE))

```

## Data cleaning
As demonstrated by the table above, there are a multiple rows that do not contain actors and/or actresses, we delete these. This also helps to remove duplicate rows.

```{r}
starPowerClean <- starPower %>%
  filter(category == 'actor')
```

Next we remove duplicate rows

```{r}
starPowerClean <- starPowerClean %>%
  distinct(primaryName, Rank, earnings, .keep_all = TRUE)
```

Now we again look at some descriptive statistics of the cleaned dataset

```{r}
starPowerClean %>%
  summarize(min_rank = min(Rank),
            max_rank = max(Rank),
            min_earnings = min(earnings),
            max_earnings = max(earnings))
```

## Creating the new variable:
Finally we create the new dummy variable where 1 = super star (Top 100 based on the rank) and 0 = not a superstar

```{r}
starPowerClean <- starPowerClean %>%
  mutate(superstar = ifelse(Rank <= 100, 1, 0))
```


