---
title: "Adding starpower"
output: html_document
date: "2023-09-21"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Loading libraries

```{r cars}
library(tidyverse)
library(dplyr)
```

## Loading the file
The file has been provided by my thesis supervisor. The data is scraped from... in ...

```{r}

starPower <- read_csv("../../data/datasets/superstar_persons.csv")

```

##Getting a feel for the data
We find a few noteworthy points:
* First of all we find that the rank does not matchup with the number of variables.
* Some names appear multiple times, hower with different identifiers. This suggests that a person has fulfilled different roles and therefore gets another identifier. 

```{r}
starPower %>%
  summarize(min_rank = min(Rank),
            max_rank = max(Rank),
            min_earnings = min(earnings),
            max_earnings = max(earnings))
```

## Finding duplicate rows 

```{r}

starPower %>%
  group_by(primaryName, Rank, earnings) %>%
  filter(n() > 1)

```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
