---
title: "Team 8 R Markdown Document"
output: html_document
date: "2023-09-12"
author: 'Kay van der Linden, Lex Vogels, Floris van Berloo, Thomas Gadellaa, Mehmet Eren Erdoğan'
---

# Group 8 Imdb Ratings Markdown

## Introduction

This is the Markdown document for group 8. Each member contributed on the markdown and did their own analysis about imdb datasets. After each individual presented their analysis, a joint markdown file is created.

## Pre - Analysis

Loading the `tidyverse` package:

```{r setup, echo = F, warning = F, error = F, message = F}
library(tidyverse)
```

### Comment lex 8-10-23, Do we need to create a cell here that downloads all the datasets?


### Comment lex 8-10-23, I think this function can be deleted out of the report right?

If you have your current working directory where your markdown file is, `setwd('../../data/dataset1')` should direct you to the databases. But since each database is in another folder, a function can come handy.

```{r}
wd_changer <- function(x) {
  wd <- str_c('../../data/dataset', x)
  setwd(wd)
} #I think this easy function is pretty self-explanatory.

#Let's try if the function works.

wd_changer(0)

getwd() 

#Apparently, it does!

``` 


***Dataset: title.basics ***

```{r message=FALSE, warning=FALSE}

wd_changer(2) #My file is at the second database folder. 

### If the function is deleted this one can also be deleted



title_basics <- read_tsv('../../data/title.basics.tsv.gz', n_max = 200)
#Loading only first 200 rows of the data just for exploratory data analysis.

```

**After this first step, let's take a look at the variables and produce some explanatory plots**
### Comment lex 8-10-23, above is stated that some explanatory plots will be created, but there are none created below right?

```{r}

dim(title_basics)

str(title_basics)

summary(title_basics)

```
**In this dataset, there are 9 columns**

column 1: tconst 
*This is a identifier tag which other tables also possess* 
column 2: `titleType` 
*Read this in as a character column but can also be treated as a **factor**. It contains information about the type of the visual product such as a short-movie, a series or a movie*
column 3: primaryTitle
*This is a character column for the final title that the visual product was released in*
column 4: originalTitle
*This is also a character column but it is the first title that the visual product had. It might contain foreign language titles or the original title draft before it got changed to something else*
column 5: isAdult
*This is a numeric variable which tells if the product is for adults or not. If it is for adults, the value is '1'. If not, the value is '0' *
column 6: startYear:
*This is the release year of the product. This prototype only includes earliest years so maximum and minimum values can be obtained if the whole database is loaded in*
column 7: endYear
*this character column is only viable for TV Series. It keeps track how many years that the series has lasted. For all other media, the value is '\N'*
column 8: runtimeMinutes
*This is a character column but **it should actually be a numeric one**. It represents how long the product is*
column 9: genres
*This is a character column that includes an array of values. A column containing two values is not recommended for a tidy dataset and thus, the values should be filtered and separated for further analysis*

###comment lex 08-10-23, Do we want to include what is underneath this comment? I think it should be modified to have the same construct as the "main takeaways" of the other datasets 


####Main Takeaways

* titleType can be converted into a factor,
* isAdult should be filtered while doing further analysis,
* endYear is unnecessary for movies,
* runtimeMinutes should be converted into an integer,
* genres should be filtered and split for a tidier frame.




***Dataset: title_ratings ***

```{r}
title_ratings <- read_tsv("../../data/title.ratings.tsv.gz")
# we are loading the whole dataset as we can make some plots
```
```{r}
view(title_ratings)
```

**In this dataset, there are 3 columns**
column 1: tconst
*this is the identifier, each cell represents 1 serie/film*
column2: averageRating
*this is the averga rating the serie/film got*
column 3:num_votes
*This is the number of votes that contributed to the rating of the series or movie*

**summary statistics about the variables : average rating and number of votes**
```{r}
summary(title_ratings$averageRating)
summary(title_ratings$numVotes)

```

**A histogram with the distribution of the averga ratings**
```{r}
hist(title_ratings$averageRating, main = "Distribution of Average Ratings", xlab = "Average Rating")
```

**Boxplot number of votes** 

### comment lex 08-10-23, I think we can delete this one right?I do not know if this is really valuable.
```{r}
boxplot(title_ratings$numVotes, main = "Box Plot of number of votes")
```


**scatter plot of the relationship between the average rating and the nuber of votes**
```{r}
plot(title_ratings$averageRating, title_ratings$numVotes, main = "Scatter Plot: Average Rating vs. Vote Count", 
     xlab = "Average Rating", ylab = "Vote Count", pch = 16, col = "black")
```

**Main takeaways**
* The variable Tconst can be used to merge this data set with the other datasets
* looking at the plots, the variables 'averge rating' and 'number of votes' seems to be positively correlated


###Comment lex 8-10-23 this whole section below can be deleted right? As we do not use this dataset.

reading the data set: title_basics_ratings (Thomas)
reading the data set: title_principles (Thomas)


```{r}
title_principals <- read_tsv("../../data/title.principals.tsv")
```

```{r}
view(title_principals)
```

Some calculations and code to get a feel for the dataset
```{r}
# Display unique values in the 'job' column
unique_jobs <- unique(title_principals$job)

# Count how many times each unique value appears
job_counts <- table(title_principals$job)

# Create a data frame to display the results
job_counts_df <- data.frame(Job = unique_jobs, Count = job_counts)

# Print the unique job values and their counts
print(job_counts_df)

```

Next we look at the number of unique titles that are in the dataset

```{r}
# Calculate the number of unique values in the 'tconst' column
num_unique_tconst <- length(unique(title_principals$tconst))

# Print the number of unique 'tconst' values
print(num_unique_tconst)
```

We do the same for the crew of the titles
```{r}
# Calculate the number of unique values in the 'nconst' column
num_unique_nconst <- length(unique(title_principals$nconst))

# Print the number of unique 'nconst' values
print(num_unique_nconst)
```

**In this dataset, there are 6 columns**

1. 'tconst' is a unique alphanumeric identifier assigned to a movie. This identifier can be used in order to merge with other datasets provided by IMDb. There are 9,095,203 unique titles in this dataset.
2. 'ordering' refers to a number to uniquely identify rows for a given titleId. 
3. 'nconst' is similar to the 'tconst', the only difference is that the 'nconst' identifies crew/cast. There are 5,088,146 unique persons in this dataset.
4. 'job' refers to the job of the person ('nconst') fullfiled in a specific title ('tconst').
5. 'characters' shows the name of the character that is played by the respective person. If this is inapplicable the given value is '\N'

**Main takeaways**
This dataset does not consit of any variable that, on it self, ads to the relevance of our research. However, this dataset could serve a purpose in merging different IMDb datasets. 



**Dataset: title_name_basics**
```{r setup, include = FALSE}

title_name_basics <- read_tsv("name.basics.tsv.gz", n_max = 200)
#Loading only first 200 rows of the data just for exploratory data analysis.
View(title_name_basics)
summary(title_name_basics)

```

**In this dataset, there are 6 columns**

Column 1: nconst
*this is the identifier*
Column 2: primaryName
*is a character variable that states the full name of the person that contributed to a certain movie or series*
Column 3: birthYear
*is a numeric variable containing the year of birth from a person*
Column 4: deathYear
*is a numeric variable containing the year of passing. if the return value is /N, this means the person is still alive*
Column 5: primaryProfession
*this is de profession of the person. some people have multiple professions, which are all stored in one column. the columns are separated by comma's*
Column 6: knownForTitles
*these are the ID's of the movies the person participated in, stored in one column separated by comma's. these title ID's can also be found in the title_name_basics dataset.* 

**Main takeaways**
* In order to sample for actress/actor only, the primaryProfession column should be filtered
* In order to connect this datatable to the title_name_basics datatable, the knownForTitles column should be destringed
* birthYear and deathYear are not relevant for this research



