---
title: "Linear_regression"
output: html_document
date: "2023-10-06"
author: 'Team 8'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Before starting the linear regression, we are going to load the final megred dataset and summarize it

```{r}
library(tidyverse)
final_merged_dataset <- read_tsv ("../../data-preparation/output/final_merged_dataset.tsv")
final_merged_dataset 
summary(final_merged_dataset)
```

When you take a look at the output, you'll notice that there are dummy variables for certain category's. We have created these dummy's because those are the most often occurring genres in the dataset.


# We will now proceed to perform a linear regression on the final dataset
```{r}

formula <- averageRating ~ numVotes + mean_ranking + time_since_release + is_superstar + Drama + Comedy + Documentary + Romance + Action + Other

dataset_lm1 <- lm(formula, final_merged_dataset)
summary(dataset_lm1)

```

When looking at the output, we notice that all the variables have a significant effect on the average rating except Comedy genre.

# Assumptions
In order to check for assumptions, we run a Kolmogorov Smirnov test to test for normality, and a Durbin-Watson test to check if the residuals are correlated

```{r}
# Normality
ks.test(dataset_lm1$residuals, "pnorm", mean=mean(dataset_lm1$residuals), sd=sd(dataset_lm1$residuals))

# Multicolinearity
library(car)
durbinWatsonTest(dataset_lm1)

# Homoscesdasticity

plot(dataset_lm1, which = 1)
```

The output of the Kolmogorov-Smirnov test shows us that we can reject the null-hypothesis, which means that the data is not normally distributed. After running the durbinWatson test, we fail to reject the null-hypothesis, which means that the residuals are not autocorrelated. Finally, the assumption of the homoscesdasticity is not met when we look at the residuals plot.

# Scatter plot of predicted vs actual values

In our final part of the linear regression analysis, we check how our model performs at prediciting the average rating, compared to the actual average rating

```{r}
# Predicted values from the model
predicted_lm <- predict(dataset_lm1)

final_merged_dataset_nona <- final_merged_dataset %>% drop_na()

# Create a scatterplot
plot(final_merged_dataset_nona$averageRating, predicted_lm, xlab = "Actual", ylab = "Predicted", main = "Predicted vs. Actual")
abline(0, 1, col = "red")  # Add a 45-degree reference line
```


When we take a look at the scatter plot, we can conclude that our model doesn't perform well with predicting the average rating. What's even more strange, is that our model predicts ratings higher than 10, which isn't possible.

After realizing that neither the assumptions nor the predictions align, we decided to transform the dependent variable for a final glimpse. The calculation of the RMSE will be useful to compare the difference.

# Transformations

```{r}

# Transformations of the dependent variable

final_merged_dataset$sqrt_averageRating <- sqrt(final_merged_dataset$averageRating)

final_merged_dataset$log_averageRating <- log(final_merged_dataset$averageRating)

final_merged_dataset$mc_averageRating <- (final_merged_dataset$averageRating - mean(final_merged_dataset$averageRating)) / sd(final_merged_dataset$averageRating)

transformed_data <- boxcox(averageRating ~ 1, data = final_merged_dataset)

lambda <- transformed_data$x[which.max(transformed_data$y)]

final_merged_dataset$boxcox_averageRating <- (final_merged_dataset$averageRating^lambda - 1) / lambda

# Formulas

formula_sqrt <- sqrt_averageRating ~ numVotes + mean_ranking + time_since_release + is_superstar + Drama + Comedy + Documentary + Romance + Action + Other

formula_log <- log_averageRating ~ numVotes + mean_ranking + time_since_release + is_superstar + Drama + Comedy + Documentary + Romance + Action + Other

formula_mc <- mc_averageRating ~ numVotes + mean_ranking + time_since_release + is_superstar + Drama + Comedy + Documentary + Romance + Action + Other

formula_boxcox <- boxcox_averageRating ~ numVotes + mean_ranking + time_since_release + is_superstar + Drama + Comedy + Documentary + Romance + Action + Other

# Models

model_sqrt <- lm(formula_sqrt, data = final_merged_dataset)

model_log <- lm(formula_log, data = final_merged_dataset)

model_mc <- lm(formula_mc, data = final_merged_dataset)

model_boxcox <- lm(formula_boxcox, data = final_merged_dataset)

# Taking a look at the models

summary(model_sqrt)

summary(model_log)

summary(model_mc)

summary(model_boxcox)

```
# Reading the model

We've tried square root, log, mean centering and box-cox transformations and the highest R squared is obtained via the box-cox transformation. It suits because there is a heteroscasdisticity and a not normally distributed dependent variable. Yet, 0.19 is not that much of a fulfilling score.

When we read the model, the mean_ranking and is_superstar variables are in a negative relationship with the dependent variable. In addition, Romance and Action genres also impact the averageRating negatively.


# Conclusion

* High rated movies are the ones with high numbers of votes, long time since release, in the genres of drama, comedy or documentary.

* Ranking of the actor or if the actor is a superstar has a negative effect on the averageRating. In addition, genres of Romance, Action and Other also pull the averageRating of a movie down.

# Limitations

The NA values are left unbothered. They could've been imputed or removed.

The bollywood movies are not filtered out. This might explain the negative relationship between mean_ranking and is_superstar variables.

